%%%%
% MTecknology's Resume
%%%%
% Author: Michael Lustfield
% License: CC-BY-4
% - https://creativecommons.org/licenses/by/4.0/legalcode.txt
%%%%

\documentclass[letterpaper,10pt]{article}
%%%%%%%%%%%%%%%%%%%%%%%
%% BEGIN_FILE: mteck.sty
%% NOTE: Everything between here and END_FILE can
%% be relocated to "mteck.sty" and then included with:
%\usepackage{mteck}

% Dependencies
% NOTE: Some packages (lastpage, hyperref) require second build!
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{bookmark}
\usepackage{lastpage}

% Sans-Serif
%\usepackage[sfdefault]{FiraSans}
%\usepackage[sfdefault]{roboto}
%\usepackage[sfdefault]{noto-sans}
%\usepackage[default]{sourcesanspro}

% Serif
\usepackage{CormorantGaramond}
\usepackage{charter}

% Colors
% Use with \color{Name}
% Can wrap entire heading with {\color{accent} [...] }
\usepackage{xcolor}
\definecolor{accentTitle}{HTML}{0e6e55}
\definecolor{accentText}{HTML}{0e6e55}
\definecolor{accentLine}{HTML}{a16f0b}

% Misc. Options
\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\urlstyle{same}

% Adjust Margins
\addtolength{\oddsidemargin}{-0.7in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-0.7in}
\addtolength{\textheight}{1.4in}

\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\setlength{\tabcolsep}{0pt}
\setlength{\footskip}{3.7pt}
\raggedbottom
\raggedright

% ATS Readability
\input{glyphtounicode}
\pdfgentounicode=1

%-----------------%
% Custom Commands %
%-----------------%

% Centered title along with subtitle between HR
% Usage: \documentTitle{Name}{Details}
\newcommand{\documentTitle}[2]{
  \begin{center}
    {\Huge\color{accentTitle} #1}
    \vspace{10pt}
   
    \vspace{2pt}
    %\footnotesize\color{accentTitle} #2}
    \footnotesize{#2}
    \vspace{2pt}
  
  \end{center}
}

% Create a footer with correct padding
% Usage: \documentFooter{\thepage of X}
\newcommand{\documentFooter}[1]{
  \setlength{\footskip}{10.25pt}
  \fancyfoot[C]{\footnotesize #1}
}

% Simple wrapper to set up page numbering
% Usage: \numberedPages
% WARNING: Must run pdflatex twice!
\newcommand{\numberedPages}{
  \documentFooter{\thepage/\pageref{LastPage}}
}

% Section heading with horizontal rule
% Usage: \section{Title}
\titleformat{\section}{
  \vspace{-5pt}
  \color{accentText}
  \raggedright\large\bfseries
}{}{0em}{}[\color{accentLine}\titlerule]

% Section heading with separator and content on same line
% Usage: \tinysection{Title}
\newcommand{\tinysection}[1]{
  \phantomsection
  \addcontentsline{toc}{section}{#1}
  {\large{\bfseries\color{accentText}#1} {\color{accentLine} |}}
}

% Indented line with arguments left/right aligned in document
% Usage: \heading{Left}{Right}
\newcommand{\heading}[2]{
  \hspace{10pt}#1\hfill#2\\
}

% Adds \textbf to \heading
\newcommand{\headingBf}[2]{
  \heading{\textbf{#1}}{\textbf{#2}}
}

% Adds \textit to \heading
\newcommand{\headingIt}[2]{
  \heading{\textit{#1}}{\textit{#2}}
}

% Template for itemized lists
% Usage: \begin{resume_list} [items] \end{resume_list}
\newenvironment{resume_list}{
  \vspace{-7pt}
  \begin{itemize}[itemsep=-2px, parsep=1pt, leftmargin=30pt]
}{
  \end{itemize}
  %\vspace{-2pt}
}

% Formats an item to use as an itemized title
% Usage: \itemTitle{Title}
\newcommand{\itemTitle}[1]{
  \item[] \underline{#1}\vspace{4pt}
}

% Bullets used in itemized lists
\renewcommand\labelitemi{--}

%% END_FILE: mteck.sty
%%%%%%%%%%%%%%%%%%%%%%


%===================%
% John Doe's Resume %
%===================%

%\numberedPages % NOTE: lastpage requires a second build
%\documentFooter{\thepage of 2} % Does similar without using lastpage
\begin{document}

  %---------%
  % Heading %
  %---------%

\documentTitle{Meet Shah}{
    % Web Version
    %\raisebox{-0.05\height} \faPhone\ [redacted - web copy] ~
    %\raisebox{-0.15\height} \faEnvelope\ [redacted - web copy] ~
    %%
    \href{tel:7149878734}{
      \raisebox{-0.05\height} \faPhone\ \, \textbf{(714) 987-8734}} ~  ~
    \href{mailto:meet2506@outlook.com}{
      \raisebox{-0.15\height} \faEnvelope\ \, \textbf{meet2506@outlook.com}} ~  ~
    \href{https://www.linkedin.com/in/meet-s-shah/}{
      \raisebox{-0.15\height} \faLinkedin\ \, \textbf{/meet-s-shah}} ~  ~
    \href{https://github.com/meets2506}{
      \raisebox{-0.15\height} \faGithub\ \, \textbf{/meets2506}} ~  ~
      \raisebox{-0.15\height} \faMapMarker\ \, \textbf{Los Angeles, CA} (Open for Relocate)}
  


  %---------%
  % Summary %
  %---------%

  %\tinysection{Summary}
  %Simplified version of a monstrosity that I built back in college using current best practices.

  %-----------%
  % Education %
  %-----------%

  \section{Education}

  \headingBf{\faUniversity California State University Long Beach }{Jan'23 - Dec'24} % Note: Adding year(s) exposes an implied age
  \headingIt{Master of Science in Computer Science | \textbf{GPA : 3.5/4}}{Long Beach, CA}
 % \headingIt{Minors: Networking ; Network Security}{}

   \vspace{6pt}

 \headingBf{\faUniversity Gujarat Technological University}{Aug'18 - May'22} % Note: Adding year(s) exposes an implied age
  \headingIt{Bachelor of Engineering in Computer Engineering | \textbf{GPA : 3.69/4}}{Ahmedabad, India}

 % \headingBf{Certifications}{}
 % \begin{resume_list}
  %  \item Salt \hspace{2pt}- SaltStack Certified Engineer
   % \item GCP - Professional Cloud Architect
  %\end{resume_list}

  %------------%
  % Experience %
  %------------%

\section{Experience}

  \headingBf{\faBriefcase Softvan Pvt Ltd}{Feb'22 -- Dec'22}
\headingIt{Software Engineer}{Ahmedabad, India}
\begin{resume_list}
  \item \textbf{45\% Embedded Systems \& Qualcomm Development:} 
  Engineered software solutions for Qualcomm QC 8550 and 6490 boards, leveraging advanced compiler optimizations for BERT-based and other LLM workloads. Accelerated AI/ML pipelines on HTP and Adreno GPUs to enhance performance and efficiency.

  \item \textbf{30\% Cross-Platform \& Android Build Systems:} 
  Built, compiled, and deployed ARM-based applications on Windows, macOS, and x86 platforms using cross-compilation toolchains. Ensured seamless integration with Android build systems, optimizing for diverse hardware environments.

  \item \textbf{25\% Machine Learning \& System Optimization:} 
  Implemented inference techniques for large language models (LLMs), including BERT and Retrieval-Augmented Generation (RAG). Optimized AI/ML pipelines for scalability, reduced latency, and efficient resource utilization across multiple architectures.
  \vspace{3pt}
\end{resume_list}


  \headingBf{\faBriefcase iClerisy Solutions}{Jun'21 - Jan'22}
  \headingIt{Embedded Software Developer}{Ahmedabad, India}
  \begin{resume_list}
    \item \textbf{40\% Low-Level Programming \& Debugging:} Developed and debugged C/C++ applications for embedded systems, optimizing UNIX-based tools and libraries for high-performance computing.
    \item \textbf{35\% AI/ML Integration \& Model Deployment:} Integrated deep learning models into embedded platforms, fine-tuning performance for Qualcomm hardware accelerators.
    \item \textbf{25\% System Architecture \& Performance Tuning:} Enhanced system-level optimization for AI-driven applications, utilizing Qualcomm’s software ecosystem and tools to improve execution efficiency.
  \end{resume_list}






  %----------------------------%
  % Extracurricular Activities %
  %----------------------------%

  \section{Projects}

  \headingBf{Medical Fraud Detection System}{}
  \begin{resume_list}
    \item Built and launched a web-based fraud detection system using Python, Flask, and MySQL, improving
    detection accuracy by 35\% through machine learning algorithms and data analysis tools like Pandas and
    NumPy to streamline fraud identification.
    \item Created a responsive UI with JavaScript, HTML, and CSS, enhancing user interaction and streamlining data
    visualization with Matplotlib for faster and more accurate decision-making.
  \end{resume_list}

  \headingBf{ResourceHub}{}
  \begin{resume_list}
    \item Built a web application using React.js, Python, Flask, and Postgres, implementing the Hungarian algorithm
    to optimize team allocation, improving project efficiency and resource distribution.
    \item Integrated Flexible visual insights with Material UI, streamlining onboarding processes by 30\% and
    enabling data-driven decision-making for team management.
  \end{resume_list}

   \headingBf{WaterWise IoT Device}{}
  \begin{resume_list}
    \item Engineered a smart water intake monitoring device using Python 3, Django, and MySQL, supporting efficient
    data handling and real-time monitoring with intuitive user interfaces.
    \item Programmed an ESP32 chip in C++ using Arduino IDE, integrating strain gauges for precise weight
    measurements and enabling Wi-Fi connectivity for cloud-based storage and remote sensor data analysis.
  \end{resume_list}

  
  %--------%
  % Skills %
  %--------%

  \section{Skills}

\begin{itemize}[itemsep=-2pt, parsep=2pt, leftmargin=130pt, labelwidth=120pt, align=parleft]
    \item[\textbf{Languages/Databases}]
    Java, Python, JavaScript, MongoDB, PostgreSQL, MySQL, C, C++

    \item[\textbf{Frameworks/Libraries}]
    Flask, Django, Pandas, NumPy, Matplotlib, PyTorch, TensorFlow, Selenium, 
    PyTest, SonarQube, Qualcomm Hexagon SDK

    \item[\textbf{Developer Tools/Cloud}]
    Git, Jira, Docker, GitHub, VS Code, PyCharm, IntelliJ, Android JDK, Qualcomm QXDM, SNPE

    \item[\textbf{Key Strengths}]
    Collaboration, Leadership, Strategic evaluation, Resolving challenges, Flexibility
\end{itemize}



  

\end{document}